Matching Bullets

### 2015-12-03 imaging-paper.Rnw
start of discussing the automated matching algorithm

\hh{XXX next step: how does this matching work in known non-matches? distribution of CMS under a null of no match? }

>>>>

\hh{The automated matching routine is then as follows:
Identify a stable region for each bullet and pick the lowest crosscut level in this region (assumption here: lower crosscut levels show better expression of individual marks XXX need to still check)

All of the other steps are done on pairs of bullets:
\begin{enumerate}
\item Smooth the two crosscuts by a loess with a very small span. 
\item Use cross-correlation to find the best alignment along the crosscuts: Shift one of the crosscuts by the lag indicated by the cross-correlation function.
\item Based on a starting threshold level of $\theta$, identify the maximal number of CMS (consecutive matching striae) between the two crosscuts. Vary $\theta$, such that the maximum number of CMS is reached. 
\end{enumerate}
}
\hh{XXX next step: how does this matching work in known non-matches? distribution of CMS under a null of no match? }
